Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
intro

\section{Motivation}
\label{motivation}

@@

A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
It does not make sense to determine the severity of constraint violations of an entire constraint type,
as the severity of the violation of a given constraint depends on the individual context and vocabulary.
%as the violation of one constraint may be severe,
%whereas, the violation of another constraint of the same type may be minor.
\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
%\begin{itemize}
	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
%\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
They are not seen as serious errors.
\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
\emph{Warnings} are syntactic or semantic errors which typically should not lead to an abortion of data processing.
%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong (\emph{error}) and 
in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality.

@@

The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
%Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
%The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g. \emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
Depending on property datatypes, two different literal values have
a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
	&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
	&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
	&\ms{CategoryStatistics $\equiv$} \\
	&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}
 \}\\ 
\end{DL}
\end{center}
\tb{K einführen}
All properties, not having the same domain and range types, are defined to be pairwise disjoint
(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
i.e., individuals cannot be instances of multiple disjoint classes.
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}). 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
which may indicate when the data is verbose/redundant or expressed at a too general level.

@@

\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
\begin{DL}
$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
\end{DL}

A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
\begin{DL}
Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
\end{DL}

%\textbf{Existential Quantifications.}
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
\begin{DL}
Variable $\equiv$ $\exists$ concept.Concept
\end{DL}
%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
%Case quantity measures how many cases are collected for a study.
%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).

%\textbf{Cardinality Restrictions on Properties.}
%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
\begin{DL}
TableStructure $\sqsubseteq$ $\geq$1 column.Column \\
Variable $\sqsubseteq$ $\leq$1 concept.Concept \\
DataSet $\sqsubseteq$ $\geq$1 structure.DSD $\sqcap$
$\leq$1 structure.DSD
\end{DL}

@@

%\section{Basic Constraint Types}
%\label{vocabulary-constraint-types}
%As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
%Reasoning and validation are indeed very closely related. 
%\emph{Reasoning} is the process of determining what follows from what has been stated.
%%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
%We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
%\begin{enumerate}
	%\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).  
  %\item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
%\end{enumerate}
%\subsection{Basic Constraint Types with Reasoning}
%\label{basic-constraint-types-with-reasoning}
%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
%Reasoning as an optional pre validation step is beneficial for RDF validation as 
%(1) it may resolve constraint violations and  
%(2) it may cause useful constraint violations.
%A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly. For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
 %&\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
 %%&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
 %&\ms{LogicalDataSet( logical-data-set )},\\
 %&\ms{aggregation( logical-data-set, aggregated-data-set )}
 %\}\\ 
%\end{DL}
%\end{center}
%As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
%{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
%and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
%we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
%As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
%If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred. 
%Reasoning may also cause constraint violations which are needed to enhance data quality.
%With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
%i.e., each person-level data set is also a catalog data set.
%Thus, constraints on catalog data sets are also validated for person-level data sets;
%e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution: 
%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ 
 %&\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
%&\ms{Variable $\equiv$ $\exists$ concept.Concept}
 %\}\\ 
%\end{DL}
%\end{center}
%We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
%%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
%%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
%%Case quantity measures how many cases are collected for a study.
%%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ 
  %&\ms{fundedBy $\sqsubseteq$ contributor}
 %\}\\ 
%\end{DL}
%\end{center}
%By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
%the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
%a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
%If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
%%fundedBy $\sqsubseteq$ contributor
%%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}. 
%%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
%%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
%%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
%%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
%%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
%%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
%%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
%%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
%%$\mathcal{K}=\{$ 
  %%&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
	%%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
	%%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
	%%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
 %%\}\\ 
%%\textbf{Cardinality Restrictions on Properties.}
%%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
%%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
%%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
%%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
%%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
%%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
%%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-

>>>>

\subsection{Motivation}
\label{motivation}

@@

A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
It does not make sense to determine the severity of constraint violations of an entire constraint type,
as the severity of the violation of a given constraint depends on the individual context and vocabulary.
%as the violation of one constraint may be severe,
%whereas, the violation of another constraint of the same type may be minor.
\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
%\begin{itemize}
	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
%\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
%They are not seen as serious errors.
\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
\emph{Warnings} are syntactic or semantic errors which typically should not lead to an abortion of data processing.
%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong (\emph{error}) and 
in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality.

@@

The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
%Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
%The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g. \emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
Depending on property datatypes, two different literal values have
a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
Consider the following \emph{DL} knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly. For simplicity reasons, we do not state namespace prefixes in DL statements.}:
\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
	&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
	&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
	&\ms{CategoryStatistics $\equiv$} \\
	&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}
 \}\\ 
\end{DL}
\end{center}

All properties, not having the same domain and range types, are defined to be pairwise disjoint
(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
i.e., individuals cannot be instances of multiple disjoint classes.
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}). 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
which may indicate when the data is verbose/redundant or expressed at a too general level.

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ &\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
&\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}, \\
&\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}, \\
&\ms{Variable $\equiv$ $\exists$ concept.Concept}
\}\\ 
\end{DL}
\end{center}

@@

We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.

A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%\begin{DL}
%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%\end{DL}
Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}.
\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}.
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
%Case quantity measures how many cases are collected for a study.
%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).

%\textbf{Cardinality Restrictions on Properties.}
%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
%\begin{DL}
%TableStructure $\sqsubseteq$ $\geq$1 column.Column \\
%Variable $\sqsubseteq$ $\leq$1 concept.Concept \\
%DataSet $\sqsubseteq$ $\geq$1 structure.DSD $\sqcap$
%$\leq$1 structure.DSD
%\end{DL}

@@

\section{Basic Constraint Types}
\label{vocabulary-constraint-types}

%As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
%Reasoning and validation are indeed very closely related. 
%\emph{Reasoning} is the process of determining what follows from what has been stated.
%%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
%We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
%\begin{enumerate}
	%\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).  
  %\item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
%\end{enumerate}

\subsection{Basic Constraint Types with Reasoning}
\label{basic-constraint-types-with-reasoning}

%%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
%%Reasoning as an optional pre validation step is beneficial for RDF validation as 
%%(1) it may resolve constraint violations and  
%%(2) it may cause useful constraint violations.
%A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%%\begin{DL}
%%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%%\end{DL}
%Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly. For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
%
%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
 %&\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
 %%&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
 %&\ms{LogicalDataSet( logical-data-set )},\\
 %&\ms{aggregation( logical-data-set, aggregated-data-set )}
 %\}\\ 
%\end{DL}
%\end{center}
%
%As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
%{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
%and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
%we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
%As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
%If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred. 
%
%Reasoning may also cause constraint violations which are needed to enhance data quality.
%With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
%i.e., each person-level data set is also a catalog data set.
%Thus, constraints on catalog data sets are also validated for person-level data sets;
%e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
 &\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
&\ms{Variable $\equiv$ $\exists$ concept.Concept}
 \}\\ 
\end{DL}
\end{center}

We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
%Case quantity measures how many cases are collected for a study.
%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).

\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
  &\ms{fundedBy $\sqsubseteq$ contributor}
 \}\\ 
\end{DL}
\end{center}

By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.

%\begin{DL}
%fundedBy $\sqsubseteq$ contributor
%\end{DL}

%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}. 
%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).

%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
%\begin{DL}
%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
%\end{DL}

%\begin{center}
%\begin{DL} 
%$\mathcal{K}=\{$ 
  %&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
	%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
	%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
	%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
 %\}\\ 
%\end{DL}
%\end{center}
